Acoustic Scene Classification: \\ Supervised and Unsupervised Approaches using the Scattering Transform

### 2016-06-21 paper/structureScene.tex
define \ie
minor changes at the beginning of Section III

\usepackage{pgf}
\usepackage{tikz}
\usetikzlibrary{arrows,positioning}
\usepackage{url}
\usepackage{color}
\usepackage{xspace}
\newcommand*{\eg}{e.g.\@\xspace}

@@

\section{Scattering transforms}
Scattering transforms are a multiscale representations of audio signals which cascade an auditory filterbank and a modulation filterbank, interspersed with complex modulus nonlinearities.
Depending upon the chosen architecture, the modulation filterbank may either be performed solely over the time variable or on both time and frequency.
In this section, we present both the temporal scattering transform and the time-frequency scattering transform.

\subsection{Invariance and stability in acoustic scene classification}
The notion of invariance to translation plays an essential role in auditory scene classification.
Indeed, the starting time of the recordings are chosen arbitrarily, and thus do not convey any information about the class.
To cancel this superfluous source of variability, signals must be mapped to a translation-invariant feature space prior to training the classifier.
From any set of descriptors -- \eg the time-frequency representation $\boldsymbol{x_1}(t,\gamma_1)$ of  a signal $\boldsymbol{x}(t)$ --
a translation-invariant representation up to time skills of duration $T$ can be simply obtained
by convolving $\boldsymbol{x_1}$ with a low-pass filter $\boldsymbol{\phi}(t)$ of cutoff frequency
set to $1/T$:
\begin{equation}
\mathbf{S_1}\boldsymbol{x}(t, \gamma_1) = (\boldsymbol{x_1} \ast \phi) (t).
\end{equation}
As a downside, the transient information in $\boldsymbol{x_1}$ at finer scales than $T$ are lost by this low-pass filtering, hence a lack of discriminability in feature space.
To address this issue, the temporal scattering transform recovers this information by convolving $x_1$ with wavelets whose center frequencies are above $1/T$ and subsequently applying complex modulus.

>>>>

\usepackage{pgf}
\usepackage{tikz}
\usetikzlibrary{arrows,positioning}
\usepackage{url}
\usepackage{color}
\usepackage{xspace}
\newcommand*{\eg}{e.g.\@\xspace}
\newcommand*{\ie}{i.e.\@\xspace}

@@

\section{Scattering transforms}
Scattering transforms are translation-invariant representations of audio signals which cascade an auditory filterbank and a modulation filterbank, interspersed with complex modulus nonlinearities.
Depending upon the chosen architecture, the modulation filterbank may either be performed solely over the time variable or on both time and frequency.
In this section, we present both the temporal scattering transform and the time-frequency scattering transform.

\subsection{Invariance and stability in acoustic scene classification}
The notion of invariance to translation plays an essential role in auditory scene classification.
Indeed, the starting time of the recordings are chosen arbitrarily, and thus do not convey any information about the class.
To cancel this superfluous source of variability, signals must be mapped to a translation-invariant feature space prior to training the classifier.
From any set of descriptors -- \eg the time-frequency representation $\boldsymbol{x_1}(t,\gamma_1)$ of  a signal $\boldsymbol{x}(t)$ --
a translation-invariant representation up to time skills of duration $T$ can be simply obtained
by convolving $\boldsymbol{x_1}$ with a low-pass filter $\boldsymbol{\phi}(t)$ of cutoff frequency
set to $1/T$:
\begin{equation}
\mathbf{S_1}\boldsymbol{x}(t, \gamma_1) = (\boldsymbol{x_1} \ast \boldsymbol{\phi}) (t).
\end{equation}
As a downside, the transient information in $\boldsymbol{x_1}$ at finer scales than $T$ are lost by this low-pass filtering, hence a lack of discriminability in feature space.
To address this issue, the temporal scattering transform recovers this information by convolving $x_1$ with wavelets whose center frequencies are above $1/T$ and subsequently applying complex modulus.
